---
title: "NHP Mitigator Comparison Report"
date: "last-modified"
date-format: D MMM YYYY HH:mm:ss
format:
  html:
    self-contained: true
    page-layout: full
    fig-width: 12
    fig-height: 10
    toc: true
    toc-depth: 3
    number-sections: true
    number-offset: 0
    grid:
      body-width: 1100px
editor: visual
execute:
  echo: false
  warning: false
resource_files:
  - data/all_params.json
  - data/all_peers.rds
  - data/mitigator groupings.xlsx
  - data/mitigator_name_lookup.csv
  - data/nee_table.rds
  - data/NHP_trust_code_lookup.xlsx
  - data/providers.json
---

```{r}
#| label: "check-env-vars"
#| results: "asis"
#| echo: false
#| message: false

required_env_vars <- c(
  "AZ_TENANT_ID",
  "AZ_STORAGE_EP",
  "AZ_STORAGE_CONTAINER",
  "NHP_ENCRYPT_KEY"
)

if (any(Sys.getenv(required_env_vars) == "")) {
  cat("One of the following environment variables was not set, so exiting \n\n")
  cat(paste("*", required_env_vars, collapse = "\n"), "\n\n")
  knitr::knit_exit() 
}
```

```{r}
#| label: attach-functions

purrr::walk(list.files("R", ".R$", , TRUE), source)
```

```{r}
#| label: read-data-azure

# Read model-run data from Azure
container <- get_container()  # relies on .Renviron variables
runs_meta <- fetch_labelled_runs_meta(container)  # exposes run_stage metadata
params <- fetch_labelled_runs_params(runs_meta, container)
```

```{r}
#| label: read-data-local
# Read local data
all_params <- jsonlite::fromJSON("data/all_params.json")
mitigator_lookup <- read_mitigator_lookup("data/mitigator_name_lookup.csv")
mitigator_groups <- read_mitigator_groups("data/mitigator groupings.xlsx")
nee <- read_nee("data/nee_table.rds")
trust_code_lookup <- readxl::read_excel("data/NHP_trust_code_lookup.xlsx")
```

```{r}
#| label: prepare-data

extracted_params <- extract_params(params)
skeleton_table <- prepare_skeleton_table(extracted_params)

dat <- populate_table(
  skeleton_table,
  extracted_params,
  mitigator_lookup,
  mitigator_groups,
  nee
)

# Heatmap-specific

sample_activity_params <- all_params$params |>
  report_params_table("activity_avoidance") |>
  dplyr::select(
    -c(
      time_profile,
      value_1,
      value_2,
      peer,
      baseline_year,
      horizon_year
    )
  )

selected_activity_mitigators <- extracted_params |> dplyr::select(-time_profile)

activity_mitigators <- sample_activity_params |>
  dplyr::left_join(
    selected_activity_mitigators,
    by = c("activity_type", "strategy", "parameter")
  )

all_schemes <- unique(activity_mitigators$peer_year) |> sort()
```

# Introduction

-   The following report can be used to compare the activity mitigator values that Trusts have selected for parameters in the NHP Inputs App.

-   The report contains graphs as well as heatmaps and searchable, filterable tables. The dataset that has been used is available to view and download as a csv file, this can be found at the end of the report.

-   The tables throughout this report may need to be scrolled sideways to view all the columns.

-   Trust codes have been used throughout to denote the different Trusts, as well as a suffix indicating their baseline and horizon years. For example, RHW_19_41 is a baseline year of 2019 and a horizon year of 2041 for the Trust RHW.

-   The report compares values from Trusts' final model runs where applicable and uses values from their initial runs where runs have not been finalised. A final run is marked in the graphics with an "\*" after the Trust Code.

# Trust Code Lookup

```{r}
#| label: "make-trust-code-lookup"
make_trust_code_lookup(dat, trust_code_lookup)
```

# Activity Avoidance

-   This section contains graphs of the activity avoidance input values. The graphs show parameters grouped by point of delivery (PoD) as well as a more granular grouping of parameters.

-   The graphs show, on the x-axis, the 80% input range that Trusts have selected in the NHP Inputs App. These are shown as a horizontal coloured line, the endpoints of which are the low and high values selected in the Inputs App. The midpoint of this range is marked by a point. This value is shown between 0 and 1. E.g. a pair of values entered in the App as 35%-45% would appear as 0.35-0.45 on the plots below.

-   If a Trust has a high value of 1, this is an assumption of no reduction to activity. If a Trust has a low value of 0, this is an assumption of a total (100%) reduction in activity.

-   If a Trust has not input a value for the mitigator then there won't be a coloured line/point for that mitigator.

-   In some cases, Trusts have input a point estimate instead of a range, or the range input is very small. This will result in the line marking the range to either not exist or to be very small. In these cases, only the midpoint is able to be seen on the graphs.

-   The y-axis shows the different Trust Codes. These have a suffix attached to them denoting the last two digits of the baseline and horizon years used for the model run.

-   The graphs are faceted. Each facet contains a different mitigator.

-   The graphs also include results from the National Elicitation Exercise (NEE). These values are shown in the graphs as a horizontal grey bar behind each point. This bar contains a darker vertical line marking the mean value for NEE. If NEE values do not exist for a parameter then no grey bar is shown.

## PoD Overview Plots

```{r}
#| label: activity-avoidance-pod-overview-plots
#| results: asis

dat_pods <- unique(dat$activity_type)
purrr::walk(dat_pods, \(dat_pod) plot_pod_transposed(dat, dat_pod))
```

## Mitigator Grouped Plots

```{r}
#| label: activity-avoidance-mitigator-grouped-plots
#| results: asis

dat_mitigators <- unique(dat$Grouping) |> sort()

purrr::walk2(
  dat_mitigators,
  8, 
  \(group, cols) plot_mitigator_group_transposed(dat, group, cols)
)
```

# Efficiencies

-   This section displays graphs of efficiencies input values.

-   This graphs in this section follows the same approach as those in the previous section. (See previous section's introductory text for explanation of graphs)

## PoD Overview Plots

```{r}
#| label: efficiencies-pod-overview-plots
#| results: asis

dat_pods <- unique(dat$activity_type)

possibly_plot_efficiencies_pod_transposed <- 
  purrr::possibly(plot_efficiencies_pod_transposed)

purrr::walk(
  dat_pods,
  \(dat_pod) possibly_plot_efficiencies_pod_transposed(dat, dat_pod)
)
```

## Mitigator Grouped Plots

```{r}
#| label: efficiencies-mitigator-grouped-plots
#| results: asis

dat_mitigators <-unique(dat$Grouping) |> sort()

possibly_plot_efficiencies_mitigator_group <- 
  purrr::possibly(plot_efficiencies_mitigator_group)

purrr::walk2(
  dat_mitigators,
  8,
  \(group, cols) possibly_plot_efficiencies_mitigator_group(dat, group, cols)
)
```

# Heat Maps

## Mitigator Binary Table

-   This heatmap shows which Trusts have Input values for each activity mitigator. If a Trust has input a value then the cell will show a "✓" with gold background. Otherwise it will show as "✕" with a grey background.

```{r}
#| label: mitigator-binary-table
#| results: asis
#| column: screen-inset

generate_binary_table_all(activity_mitigators, all_schemes)
```

## Mitigator Midpoint Table

-   The number with the larger font in each cell shows the midpoint value for each Trust and mitigator. The numbers below this in parentheses show the actual values input by the Trust.

-   The background colour of each cell depends on the size of the range of the inputs selected by the Trust for that mitigator. The smaller the range the darker the colour of the cell.

-   When a Trust has set a point estimate instead of a range, the cell will be coloured in grey and will show 'Point Estimate' in the parentheses.

-   If a Trust has not set a value for that mitigator then the cell will have no colour and will show a "✕"

```{r}
#| label: mitigator-midpoint-table
#| results: asis
#| column: screen-inset

generate_midpoint_table_all(activity_mitigators, all_schemes)
```

# Appendix

## Mitigator Lookup

```{r}
#| label: mitigator-lookup

make_mitigator_lookup(mitigator_groups)
```

## Raw Data

```{r}
#| label: raw-data

make_raw_dt(dat)
```
